\section*{Friends become Enemies}

``Good-by, Gerry.''
Faint and ineffably poignant and tender, the last words came from the cold metal
of the communicator:
``Good-bby, little sister--''

She sat motionless in the hush  that  followed,  as  thought  listening  to  the
shadow-echoes of the  words  as  they  died  away, then she turned away from the
communicator, toward the air lock, and he pulled the black lever beside him. The
inner  door of the air lock slid swiftly open, to reveal the  bare  little  cell
that was waiting for her.

``Wait, is this  really  the  end?''  Marilyn whispered, tears welling up in her
eyes.  Barton  looked  at  her  long  and  hard, contemplaiting, calculating.
``Actually, there is  another option.'' Marilyn looked up with hope in her eyes.
``We have got to make the ship lighter somehow, and we have  to do it fast if we
want to avoid the \textbf{inevitable}.''

Quickly, they \textbf{scatter}, looking for anything that could be affordable to
lose, but the ship was devoid of all objects safe for the freight. Marilyn found
a  small toolbox hidden beneath the captain's chair and was about to lob it into
the airlock when Barton \textbf{intervened}.
``Wait,   there   might   be  tools  we  can  use  to  take  my  chair   apart''

They \textbf{pored over} the  toolbox,  emptying  its  contents out all over the
floor. Their hopes dropped as  fast  as  they  rose -- The only thing inside the
toolbox was a \textbf{thin}, \textbf{flexible} yet rusty old saw blade.

Barton \textbf{cussed} loudly. Stardust had absolutely nothing disposable in it.
It  was  just\ldots  empty.  \textbf{Considerably} more  \textbf{hollow}  than a
feminist's brain in America in the year 2015.

Marilyn  and  Barton  shared  a moment of  \textbf{mutual}  frustration  when  a
horrible idea struct Marilyn.

``There's yet another way.'' she said slowly, \textbf{dubiously}.
``What way would that be?'' Barton asked.

Marilyn didn't take  her  eyes  off  of  the  saw  blade. She circled around the
location where it lay on the floor. And then it dawned on him.
``You're  crazy\ldots''  he  stammered as she \textbf{armed}  herself  with  the
sawblade.
``You're \textbf{obviously} insane! You?  Want to challenge me? I couldn't think
of anything more \textbf{violent} than fighting a girl!''

``It's  the only way'' Marilyn said, her lips pursed as thin as a  razor.
Something  changed  within her. A feeling she couldn't \textbf{dismiss}. Just  a
short while  ago  she  was prepared to give up, prepared to surrender herself to
the abyss. Not any more. She stalked closer  and  closer  to  Barton who was now
scrambling for his gun. She was \textbf{glaring}, waiting for the perfect moment.

With one smooth leap  Marilyn launched herself at Barton and sliced at his hand.
The blade connected and cut deep into his fingers,  causing  him to drop the gun
before he could fire.

Marilyn wasn't finished.  Murder was in her eyes. She slashed at him again, this
time aiming for his throat.

He never stood a chance.

Barton \textbf{collapsed} to the floor. His artery was severed and he only had a
few precious second of  consciousness  left.  He tried \textbf{crawling} towards
his gun but it was too far away.

``Not so tough anymore, huh?'' Marilyn said coldly.

